\sectionTitle{Academic Projects}{\faThumbTack}
\textbf{Stress Analysis using Finite Element Method} \hfill{January 2019 - May 2019}\\
\textbf{Guide: Prof. Yogesh M. Desai, Department of Civil Engineering} \hfill{IIT Bombay} \\
\textbf{Description:} {The project involved implementation of FEM to analyze a problem and its benchmarking with analytical solutions.}
\begin{itemize}
    \setlength\itemsep{0.7mm}
    \item  Analyzed beams subjected to uniformly distributed load and point loads using the Finite Element Method.
    \item Performed convergence study on the model by varying number, size, and aspect ratio of the elements.
    \item Benchmarked the results obtained from the analysis with the analytical solution from beam theories.
    
\end{itemize}

\textbf{Shape of Strongest Column} \hfill{July 2018 - November 2018}\\
\textbf{Guide: Prof. Gopal R. Patil, Department of Civil Engineering} \hfill{IIT Bombay} \\
\textbf{Description:} {The project was aimed at finding optimal column shapes under different loading conditions.}
\begin{itemize}
    \setlength\itemsep{0.7mm}
    \item Employed the concepts from the Euler-Bernoulli beam theory for evaluation of buckling load.
    \item Developed the governing eigenvalue problem for buckling load using geometric stiffness and element stiffness matrix. 
    \item Shape of the column was optimized under compressive load with crushing and buckling constraints for a fixed volume.
    \item Cross-sectional variation of the column along its length was obtained using Genetic Algorithm.
\end{itemize}
%https://pdfs.semanticscholar.org/40d6/4929d0eec4ed40a390d4d60b99f68b987f58.pdf 



\textbf{Facial Recognition using Artificial Neural Network (ANN)} \hfill{July 2017 - November 2017}\\
\textbf{Guide: Prof. Indu J., Department of Civil Engineering} \hfill{IIT Bombay} \\
\textbf{Description:} {The project was directed towards developing an Artificial Neural Network (ANN) based face recognition application.}
\begin{itemize}
    \setlength\itemsep{0.7mm}
    \item {Faces were localized using the Viola-Jones algorithm, followed by extraction and neural network-based face recognition.}
    \item {Developed a two-layer neural network of 100 neurons employing Gradient-based back-propagation algorithm.}
    \item {Results obtained showed an accuracy of over 80\% in recognizing input face matrices.}
\end{itemize}